### 2017-07-04 sheets/talk-10/sheet-10.tex
Extended sheet.

\begin{exercise}
  Let $\cat A$ be a locally small CCC. Use the Yoneda embedding to show that for any objects $A,B,C\in\cat A$,
  \begin{align*}
    (A\times B)^C\iso A^C\times B^C
  \end{align*}
  If $\cat A$ also has binary coproducts, show that also
  \begin{align*}
    A^{B+C}&\iso A^B\times A^C\\
    (A\times B)+(A\times C)&\iso A\times (B+C)
  \end{align*}
\end{exercise}

@@

  A functor $F\from \cat A\to\cat B$ \emph{preserves limits} if it preserves limits of shape $\mathbf I$ for all small categories $\mathbf I$.
\end{definition}
\begin{exercise}
  Fill in some of the missing details in the proof that for any small category $\cat A$ the presheaf category $[A^\op,\Set]$ is cartesian closed:
  \begin{enumerate}
  \item Show that for any $A\in\cat A$, $H_A$ preserves colimits. As a consequence $$H_A(\lim_{\to\mathbf I} D)\iso \lim_{\to\mathbf I}(H_A\of D)$$ for all shapes and diagrams.
    \hint{It suffices to show that it preserves all products and equalizers.}
  \item Let $F\from \cat A\to\Set$ be a presheaf. Show that the functor $-\times F\from [\cat A^\op,\Set]\to[\cat A^\op,\Set]$ preserves colomits. That is: For any small category $\mathbf I$ and functor $D\from\mathbf I\to [\cat A^\op,\Set]$,
    \begin{align*}
      \lim_{\to \mathbf I} (D\times F)\iso (\lim_{\to \mathbf I} D)\times F.
    \end{align*}
    You may assume that $[\cat A^\op,\Set]$ has all limits. (In particular limits, which are functors $\cat A^\op\to\Set$, are taken ``pointwise'': $$\left(\lim_{\to I\in\mathbf I} D(I)\right)(A) \iso \lim_{\to I\in\mathbf I} \left(D(I)(A)\right)$$ for all shapes and diagrams.)
    \hint{TODO}
  \end{enumerate}
\end{exercise}

\begin{exercise}
  special case of yoneda embedding: groups vs. Caley-representation
\end{exercise}

% \begin{exercise}
%   A presheaf X:C op→SetX : C^{op} \to Set is representable precisely if the comma category (Y,const X)(Y,const_X) has a terminal object. If a terminal object is (d,f:Y(d)→X)≃(d,f∈X(d))(d, f : Y(d) \to X) \simeq (d, f \in X(d)) then X≃Y(d)X \simeq Y(d).

% This follows from unwrapping the definition of morphisms in the comma category (Y,const X)(Y,const_X) and applying the Yoneda lemma to find
% (Y,const X)((c,f∈X(c)),(d,g∈X(d)))≃{u∈C(c,d):X(u)(g)=f}. (Y,const_X)((c,f \in X(c)), (d, g \in X(d))) \simeq \{ u \in C(c,d) : X(u)(g) = f \} \,.

% Hence (Y,const X)((c,f∈X(c),(d,g∈X(d)))≃pt(Y,const_X)((c,f \in X(c), (d, g \in X(d))) \simeq pt says precisely that X(−)(f):C(c,d)→X(c)X(-)(f) : C(c,d) \to X(c) is a bijection.
% \end{exercise}

>>>>

\begin{exercise}
  Recall the following re-formulation of the Yoneda principle: For any locally small category $\cat A$ and objects $A,A'\in\cat A$:
  \begin{align*}
    \cat A(B,A)\iso \cat  A(B,A')\text{ naturally in } B\in\cat A
  \end{align*}
implies $A\iso A'$. Show that naturality is really necessary.
\hint{There is a counterexample with two objects.}
\end{exercise}

\begin{exercise}
  Let $\cat A$ be a locally small CCC. Use the Yoneda embedding to show that for any objects $A,B,C\in\cat A$,
  \begin{align*}
    (A\times B)^C\iso A^C\times B^C
  \end{align*}
  If $\cat A$ also has binary coproducts, show that also
  \begin{align*}
    A^{B+C}&\iso A^B\times A^C
  \end{align*}
\end{exercise}

@@

  A functor $F\from \cat A\to\cat B$ \emph{preserves limits} if it preserves limits of shape $\mathbf I$ for all small categories $\mathbf I$.
\end{definition}
\begin{exercise}
  Fill in some of the missing details in the proof that for any small category $\cat A$ the presheaf category $[A^\op,\Set]$ is cartesian closed:
  \begin{enumerate}
  \item Show that for any $A\in\cat A$, $H_A$ preserves colimits. As a consequence $$H_A(\lim_{\to\mathbf I} D)\iso \lim_{\to\mathbf I}(H_A\of D)$$ for all shapes and diagrams.
    \hint{It suffices to show that it preserves all products and equalizers.}
  \item Let $F\from \cat A\to\Set$ be a presheaf. Show that the functor $-\times F\from [\cat A^\op,\Set]\to[\cat A^\op,\Set]$ preserves colomits. That is: For any small category $\mathbf I$ and functor $D\from\mathbf I\to [\cat A^\op,\Set]$,
    \begin{align*}
      \lim_{\to \mathbf I} (D\times F)\iso (\lim_{\to \mathbf I} D)\times F.
    \end{align*}
    You may assume that $[\cat A^\op,\Set]$ has all limits. (In particular limits, which are functors $\cat A^\op\to\Set$, are taken ``pointwise'': $$\left(\lim_{\to I\in\mathbf I} D(I)\right)(A) \iso \lim_{\to I\in\mathbf I} \left(D(I)(A)\right)$$ for all shapes and diagrams.)
    \hint{Use the fact that $[\cat A^\op,\Set]$ has all limits to deduce that there is an arrow $\lim_{\to \mathbf I} (D\times F)\to (\lim_{\to \mathbf I} D)\times F$ and use the Yoneda principle to show that this is an isomorphism.}
  \end{enumerate}
\end{exercise}
